\documentclass[12pt]{pset}

\course{Math 5801}
\author{Jim Fowler}
\date{Autumn 2015}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{arrows,chains,matrix,positioning,scopes}

\makeatletter
\tikzset{join/.code=\tikzset{after node path={%
\ifx\tikzchainprevious\pgfutil@empty\else(\tikzchainprevious)%
edge[every join]#1(\tikzchaincurrent)\fi}}}
\makeatother

\tikzset{>=stealth',every on chain/.append style={join},
         every join/.style={->}}

\newcommand{\NN}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\CP}{\mathbb{C}P}
\newcommand{\RP}{\mathbb{R}P}

\usepackage{enumerate}
\usepackage{nopageno}
\usepackage{hyperref}
\usepackage{mathrsfs}
\newcommand{\TT}{\mathscr{T}}

\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hom}{Hom}

\begin{document}
\maketitle

\noindent The exercises below should be handed in on \textit{Monday, September
  28, 2015}.  By providing well-written solutions to the problems, you
may earn up \textbf{six points.}  I encourage you to \textbf{work
  together} when solving the problems, but please write your answers
independently and include the names of your co-conspirators.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Limit points and continuity]

  Does a continuous map $f : X \to Y$ preserve limit points?  That is,
  if $x$ is a limit point of $A \subset X$, is it then the case that
  $f(x)$ is a limit point of $f(A)$?

\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Lower limit topology]

  Let $f : \RR \to \RR$ be a function with the property that
  $\lim_{x \to a^{+}} f(x) = f(a)$.  Is $f$ continuous when regarded
  as a function $\RR_\ell \to \RR$?  Here $\RR_\ell$ denotes the lower
  limit topology on $\RR$ generated by intervals of the form $[a,b)$.

\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Continuous maps are local?]

  Suppose $f : X \to Y$ is a continuous map and $A \subset X$.  Is
  $f |_A$ also continuous?  To be precise, $f|_A$ is the function
  which is the composition of the inclusion $i : A \hookrightarrow X$
  and $f : X \to Y$.

\end{problem}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Continuous maps glue]
  
  Suppose $X$ and $Y$ are topological spaces, and $A \subset X$ and
  $B \subset X$.  Suppose $f : A \to Y$ and $g : B \to Y$ are
  continuous functions which agree on $A \cap B$, so one can define a
  function $F : A \cup B \to Y$ by pasting together $f$ and $g$.

  If $F$ continuous?

\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Open maps are local?]

  Suppose $f : X \to Y$ is an open map, meaning that whenever $U$ is
  open, then $f(U)$ is an open.  Let $A \subset X$.  Is $f |_A$ also
  open?

\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Continuity and homeomorphisms]

  Suppose $f : X \to Y$ is a bijection and a continuous map, so there
  is a function $f^{-1} : Y \to X$.  Is $f^{-1}$ continuous?  Is $f$ a
  homeomorphism?

\end{problem}

\end{document}
