\documentclass[12pt]{pset}

\course{Math 5801}
\author{Jim Fowler}
\date{Autumn 2015}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{arrows,chains,matrix,positioning,scopes}

\makeatletter
\tikzset{join/.code=\tikzset{after node path={%
\ifx\tikzchainprevious\pgfutil@empty\else(\tikzchainprevious)%
edge[every join]#1(\tikzchaincurrent)\fi}}}
\makeatother

\tikzset{>=stealth',every on chain/.append style={join},
         every join/.style={->}}

\newcommand{\NN}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\CP}{\mathbb{C}P}
\newcommand{\RP}{\mathbb{R}P}

\usepackage{enumerate}
\usepackage{nopageno}
\usepackage{hyperref}
\usepackage{mathrsfs}
\newcommand{\TT}{\mathscr{T}}

\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hom}{Hom}

\begin{document}
\maketitle

\noindent The exercises below should be handed in on \textit{Monday, September
  21, 2015}.  By providing well-written solutions to the problems, you
may earn up \textbf{six points.}  I encourage you to \textbf{work
  together} when solving the problems, but please write your answers
independently and include the names of your co-conspirators.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Products and subspaces]

  Suppose $X$ and $Y$ are topological spaces and $A \subset X$ and $B \subset Y$.

  Since $A \times B \subset X \times Y$, it is possible to define a
  topology on $A \times B$ as a subspace of $X \times Y$.  How does
  this relate to the topology on $A \times B$ produced by regarding
  $A$ as a subspace of $X$, regarding $B$ as a subspace of $Y$, and
  then considering the product topology $A \times B$?  Justify the
  relationship you discover.

\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Homeomorphisms and products]

  Suppose $X$ and $Y$ are topological spaces.

  Is there a homeomorphism between $X \times Y$ and $Y \times X$?

\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Homeomorphisms and subspaces]

  Suppose $\RR$ is given its standard topology, and $\RR - \{0\}$ is
  given the topology it inherits as a subspace of $\RR$.

  Is there a homeomorphism between $\RR - \{0\}$ and $\RR$?  

  Is there a homeomorphism between $\left(\RR - \{0\}\right) \times \left(\RR - \{0\}\right)$ and $\RR \times \left(\RR - \{0\}\right)$?  

\end{problem}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Open maps]

  A function $f : X \to Y$ is a \textit{continuous map} if whenever
  $U$ is open in $Y$, then $f^{-1}(U)$ is open in $X$.  A function
  $f : X \to Y$ is an \textit{open map} if whenever $U$ is open in
  $X$, then $f(U)$ is open in $Y$.

  Is the projection $\pi_1 : X \times Y \to X$ a continuous map?  An
  open map.

\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Order topology and products]

  Define $X = (\RR,\mathcal{P}(\RR))$, i.e., $X$ is the set $\RR$
  endowed with the discrete topology.  Let $Y$ be $\RR$ given the
  order topology, and let $Y_2 = \RR \times \RR$ with the order
  topology on the lexicographic ordering.

  Relate $Y_2$ and $X \times Y$ and $Y \times Y$.

\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Order topology and subspaces]


  Let $Y$ be $\RR$ given the order topology, and let $I = [0,1]$ given
  the topology it inherits as a subspace of $Y$.

  How does $I \times I$, with the product topology, relate to the
  topology that $I \times I$ inherits as a subspace of $\RR^2$ with
  the order topology coming from the lexicographic ordering on
  $\RR^2$?

\end{problem}


\end{document}
