\documentclass[12pt]{pset}

\course{Math 5801}
\author{Jim Fowler}
\date{Autumn 2015}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{arrows,chains,matrix,positioning,scopes}

\makeatletter
\tikzset{join/.code=\tikzset{after node path={%
\ifx\tikzchainprevious\pgfutil@empty\else(\tikzchainprevious)%
edge[every join]#1(\tikzchaincurrent)\fi}}}
\makeatother

\tikzset{>=stealth',every on chain/.append style={join},
         every join/.style={->}}

\newcommand{\NN}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\CP}{\mathbb{C}P}
\newcommand{\RP}{\mathbb{R}P}

\usepackage{enumerate}
\usepackage{nopageno}
\usepackage{hyperref}
\usepackage{mathrsfs}
\newcommand{\TT}{\mathscr{T}}

\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hom}{Hom}

\begin{document}
\maketitle

\noindent The exercises below should be handed in on \textit{Monday,
  October 12, 2015}.  By providing well-written solutions to the
problems, you may earn up \textbf{six points.}  I encourage you to
\textbf{work together} when solving the problems, but please write
your answers independently and include the names of your
co-conspirators.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Irrationals and connectedness]

  Is the topological space $\R - \Q$ connected?  Here $\R - \Q$ is
  topologized as a subset of $\R$ with its standard topology.

\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Irrationals and the plane]

  Is the topological space $\R^2 - \Q^2$ connected?  Here
  $\R^2 - \Q^2$ is topologized as a subset of $\R^2$, which is itself
  given the product topology of the standard topology on $\R$.

\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Planes versus lines]

  Is $\R$ homeomorphic to $\R^2$?  Why or why not?

\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Lines versus circles]

  Is $[0,1]$ homeomorphic to $S^1 = \{ (x,y) \in \R^2 : x^2 + y^2 = 1 \}$?

\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[Graphs]

  Suppose $X$ is a connected topological space, and $f : X \to Y$ is a
  continuous map.  Is the graph of $f$, defined to be
  \[
  \{ (x,y) \in X \times Y : y = f(x) \} \subset X \times Y,
  \]
  connected?

\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}[The topologist's sine curve]

  Basically no course in point-set topology would be complete (pun
  intended) without the following example.

  Consider the function $f : \R \to \R$ given by
  \[
  f(x) = \begin{cases}
    \sin \left( \frac{1}{x} \right) & \mbox{ if $x > 0$, } \\
    0 & \mbox{ if $x \leq 0$.}
  \end{cases}
  \]
  Is the graph of $f$ connected?  Is the function continuous?

\end{problem}


\end{document}
